Carbon datasets, updated

### 2016-02-18 Rmd/carbon.Rmd
Many updates as getting ready to assemble and mask inputs
Redid Carbon stocks to correct fact that I was using veg biomass, not C, adding below ground, and re-ran through most of main-analysis up until first plots, using updated model to account for faulty grid ordering.

## Vegetation carbon
```{r, eval=FALSE}
onm <- full_path(p_devel, "veg-carbon.tif")
ext <- bbox(mgrid)[1:4]  # extent   
gdalwarp(srcfile = vcarb@file@name, t_srs = projection(mgrid), 
         dstfile = onm, r = "average", ot = "Float32", te = ext, 
         srcnodata = -32768, dstnodata = -99, tr = c(1000, 1000), 
         of = "GTiff", multi = TRUE, verbose = FALSE, overwrite = TRUE)
zvcarb <- raster(onm)  # vegetation carbon
plot(zvcarb)

@@

# then total for top 1 m
soct_1m <- calc(stack(soct[1:5]), sum)
soct_1ma <- projectRaster(soct_1m, mgrid)
writeRaster(soct_1ma, filename = full_path(p_devel, "soil-C-1m.tif"))

@@

zamcarb <- brick(stack(zvcarb, soct_1ma), 
                 filename = full_path(p_devel, "ZA-carbon.tif"))

@@

>>>>

## Vegetation carbon
```{r, eval=FALSE}
onm <- full_path(p_devel, "veg-biomass.tif")
ext <- bbox(mgrid)[1:4]  # extent   
gdalwarp(srcfile = vcarb@file@name, t_srs = projection(mgrid), 
         dstfile = onm, r = "average", ot = "Float32", te = ext, 
         srcnodata = -32768, dstnodata = -99, tr = c(1000, 1000), 
         of = "GTiff", multi = TRUE, verbose = FALSE, overwrite = TRUE)
zvbiom <- raster(onm)  # vegetation carbon

# convert to carbon and then above and below ground carbon
zvcarb <- zvbiom * 0.47  # IPCC 2006

# mean root shoot ratio, average of Mokany et al (2006) for savannas (Table 2)
# and Mugasha et al (2013), Tanzanian miombo root-shoot ratio
rooshoo <- 1 + mean(c(0.642, 0.4))
zvcarbf <- zvcarb * rooshoo
onm2 <- fp(p_devel, "veg-carbon.tif")
writeRaster(zvcarbf, filename = onm2, overwrite = TRUE)
# plot(zvcarbf - ocarb[[1]])

@@

# then total for top 1 m
soct_1m <- calc(stack(soct[1:5]), sum)
soct_1ma <- projectRaster(soct_1m, mgrid)
writeRaster(soct_1ma, filename = full_path(p_devel, "soil-C-1m.tif"), 
            overwrite = TRUE)

@@

zamcarb <- brick(stack(zvcarbf, soct_1ma), 
                 filename = full_path(p_devel, "ZA-carbon.tif"), 
                 overwrite = TRUE)

@@

## Resulting model inputs

`ZA-carbon.tif` - grid of carbon densities, for impact and prioritization
